### 2021-07-09 src/paper/report.tex
Fix abstract and add reference for global vaccination process.

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination levels that would end the
pandemic or even protect the most vulnerable\citep{Swaminathan2021}.\comment[id=HM]{Use
\url{https://www.nature.com/articles/s41562-021-01160-2} instead} In the meantime, it is
of utmost importance to employ an effective mix of strategies for containing the virus.
The most frequent initial response was a set of non-pharmaceutical interventions (NPIs)
to reduce contacts between individuals. While this has allowed some countries to sustain
equilibria with very low infection numbers,\footnote{See \citet{Contreras2021} for a
theoretical equilibrium at low case numbers which is sustained with
test-trace-and-isolate policies.} most have seen large fluctuations of infection rates
over time. Containment measures have become increasingly diverse and now include rapid
testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the
influence of seasonal patterns or of more infectious virus strains are well understood
in quantitative terms.

>>>>

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination levels that would end the
pandemic or even protect the most vulnerable \citep{Mathieu2021}. In the meantime, it is
of utmost importance to employ an effective mix of strategies for containing the virus.
The most frequent initial response was a set of non-pharmaceutical interventions (NPIs)
to reduce contacts between individuals. While this has allowed some countries to sustain
equilibria with very low infection numbers,\footnote{See \citet{Contreras2021} for a
theoretical equilibrium at low case numbers which is sustained with
test-trace-and-isolate policies.} most have seen large fluctuations of infection rates
over time. Containment measures have become increasingly diverse and now include rapid
testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the
influence of seasonal patterns or of more infectious virus strains are well understood
in quantitative terms.
